Agents and you, a brief summary

### 2015-10-28 agents/summery.tex
added configuration and operational semantics

>>>>

\subsection{Operational semantics}
Operational semantics defines the computation steps a program
configuration may take. Operational semantics allows studying
of programming constructs in a rigorous manner. It facilitates proving
general properties about a language. It lies close to the implementation
of an interpreter. It facilitates model checking.

\subsubsection{Basic syntax}
The configuration $C$ evolves into configuration $C'$:

\[C \to C'\]

If premise $P$ holds transition $C \to C'$ can be derived:

\begin{prooftree}
	\AxiomC{$P$}
	\UnaryInfC{$C \to C'$}
\end{prooftree}

\subsection{Configuration}
configurations only mention things that change.
Multi-agent configuration where $A$ is an agent and $\chi$ is the
environment:

\[\langle \{A_1, \cdots, A_n\}, \chi\rangle \]

Individual agent configuration where $i$ is the agent number, $\sigma$ the
believes, $\gamma$ the goals, $\Pi$ the plans $\theta$ the assignments and
$\xi$ the events:

\[A_i = \langle i, \sigma_i, \gamma_i, \Pi_i, \theta_i, \xi_i \rangle \]
